Borel regularity for ODEs and thimble integrals

### 2023-07-25 exp-resurgence.tex

\subsubsection{Regularity}

We generalize the result of Delabere (Lemma~3.5 \cite{diverg-resurg-iii}) to deal with fractional power singularities:

\begin{lemma}\label{lemma-3.5}
    Let $R_0>0$. Assume $f\in\mathcal{O}(\bar{D}(\infty,R_0))$ with $f(z)=O(z^{-\tau})$ at infinity for a certain $\tau\in\Q_{> 0}$, and let $M=\sup_{z\in D(\infty,R_0)} |f(z)|$. Then $\borel{f}$ is analytic on the Riemann surface of $\zeta^\tau$ and for every $\zeta$
    \begin{equation}
        |\borel{f}(\zeta)|\leq \frac{M}{\Gamma(\tau)}|\zeta|^\tau e^{\frac{|\zeta|}{R_0}}.
    \end{equation}
\end{lemma}

\begin{proof}
    The Taylor series expansion of $f$, $\sum_{k\geq 0}f_k z^{-k-\tau}$ converges in $D(\infty,R_0)$. By Cauchy inequalities, $|f_k|\leq M R_0^{-k}$ for any $k\in\Z_{\geq 0}$. The formal Borel transform of $f$ reads
    \begin{align*}
        \borel{f}(\zeta)=\frac{\zeta^{\tau-2}}{\Gamma(\tau-1)}\ast\sum_{k\geq 0} f_k \frac{\zeta^k}{k!}
    \end{align*}
   and for every $\zeta\in\C$, $\sum_{k\geq 0}|f_k|\frac{|\zeta|^k}{k!}\leq M e^{\frac{|\zeta|}{R_0}}$. Therefore
   \begin{align*}
       |\borel{f}(\zeta)|&=\Big|\frac{1}{\Gamma(\tau-1)} \int_0^\zeta (\zeta-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{t^k}{k!} dt\Big|\\
       &=\Big|\frac{\zeta^\tau}{\Gamma(\tau-1)} \int_0^1 (1-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{(\zeta t)^k}{k!} dt\Big|\\
       &\leq \frac{|\zeta|^\tau}{|\Gamma(\tau-1)|} \int_0^1 (1-t)^{\tau-1} M e^{\frac{|\zeta| t}{R_0}} dt\\
       &=M\frac{|\zeta|^\tau}{|\Gamma(\tau)|} e^{\frac{|\zeta|}{R_0}} 
   \end{align*}

   This ensures the uniform convergence on any compact set of $\C$, thus $\borel{f}$ is analytic.
   \color{Turquoise}
In the last step of the bound, we argue as follows: if $\tau>1$ then $\sup_{t\in [0,1]]}(1-t)^{\tau-1}= 1$. If $\tau\in (0,1)$ we integrate by part 
\begin{align*}
    \int_0^1 (1-t)^{\tau-1}  e^{\frac{|\zeta| t}{R_0}} dt&=-\frac{1}{\tau}(1-t)^{\tau}e^{\frac{|\zeta| t}{R_0}} \Big\vert_{t=0}^{t=1}+\frac{1}{\tau}\int_0^1(1-t)^\tau \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
    &\leq \frac{1}{\tau}+\frac{1}{\tau}\int_0^1 \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
    &=\frac{1}{\tau}+\frac{1}{\tau} e^{\frac{|\zeta| t}{R_0}}\Big\vert_{t=0}^{t=1}\\
    &=\frac{1}{\tau} e^{\frac{|\zeta| }{R_0}}
\end{align*}
   \color{black}
\end{proof}

\begin{lemma}\label{lemma-3.8}
    Let $a,b,c,m\geq 0$ and for $r=0,...,N$ let $R_r$ be a sequence of holomorphic functions in a neighborhood of infinity, real and positive on $\R^+$. Then, the convolution equation 
    \begin{equation}\label{eqn:convolution}
        \hat{W}=m+[a+b\xi]\ast\hat{W}+c \sum_{r=0}^N \borel(z^{-2}R_r(z^{-1}))\ast\hat{W}
    \end{equation}
    has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$. In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
\end{lemma}

We recall the following result which is a generalization of Lemma~3.8 in \cite{diverg-resurg-iii}:

\begin{proof}
    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution. If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization. Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
    \begin{equation}
        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a}{z}+\frac{b}{z^2}\right]\tilde{W}(z)+c\sum_{r=0}^{N}\frac{R_r(z^{-1})}{z^2}\tilde{W}(z)
    \end{equation}
    This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$). Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$. By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$. 
\end{proof}

\begin{lemma}\label{lemma-3.8bis}
    Let $a_1,a_2,...,a_d,c,m\geq 0$ and $(\hat{R}_n)_{0\leq n\leq N}$ be a sequence of entire functions, real and positive on $\R^+$ with at most exponential growth of order $1$ at infinity. Then, the convolution equation 
    \begin{equation}\label{eqn:convolution-bis}
        \hat{W}=m+[a_1+a_2\xi+...+\frac{a_d}{(d-1)!}\xi^{d-1}]\ast\hat{W}+c\left(\hat{R}_0\ast\hat{W} +\sum_{n=1}^N\hat{R}_n\ast\hat{W}^n\right)
    \end{equation}
    has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$. In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
\end{lemma}

\begin{proof}
    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution. If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization. Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
    \begin{equation}
        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
    \end{equation}
    where $R_n(z)$ \textcolor{orange}{[maybe write these as $R_n(z^{-1})$ to match statement of ODE result]} are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$. This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$). Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$. By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$. 
\end{proof}

\begin{remark}
    Lemma \ref{lemma-3.8} and \ref{lemma-3.8bis} holds also when the convolution product $\ast$ is replaced by $\ast_p$ for every $p\in\C$. 
\end{remark}

@@

\begin{theorem}\label{thm1-dim}
\textcolor{orange}{[Revise to match \texttt{reg-sing-volterra}]} In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
\begin{equation}\label{P-hat_j}
\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
\end{equation}
such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ with $\Omega$ an open sectorial domain which touches but not contains $\alpha_j$.
\end{theorem}
\begin{proof}
It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of \textcolor{orange}{\texttt{reg-sing-volterra}}.  In fact, $P(-\zeta_j-\alpha_j)=P(-\zeta)$ is a polynomial also defined at $\zeta=\alpha_j$ and by assumption $P'(-\alpha_j)\neq 0$. $Q$ is also a polynomial defined at $\zeta=\alpha_j$. Finally, assuming $R_k(z)=\sum_{j\geq 0} R_{k,j}z^j$

\begin{align*}
&\partial_{\zeta,\alpha_j}^{-2}\circ\left[R_0(\partial_{\zeta,\alpha_j}^{-1})+R_1(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)+...+R_{d-1}(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^{d-1}\right]=\sum_{\lambda\leq -2} \partial_{\zeta,\alpha_j}^\lambda\circ r_\lambda \\
&\text{ with }r_\lambda=\sum_{k=0}^{d-1} R_{k,\lambda}(-\zeta)^k.
\end{align*}

@@

Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ \footnote{Since $\sup\Lambda\leq -2$ we can assume $\varepsilon=1$ in Theorem 2.1.3 of {\tt regular Volterra}}.

@@

\begin{lemma}
 Let $\hat{\psi}_j$ be a solution of $\hat{P}_j\hat{\psi}_j=0$ for every $j=1,...,d$ and $\hat{P}_j$ defined in \eqref{P-hat_j}. If $\hat{\psi}_j$ admits a Laplace transform $\Psi_j=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j$ for $j=1,...,d$ and for a suitable direction $\theta_j$, then $\mathcal{P}\Psi_j=0$.   
\end{lemma}

@@

\begin{theorem}\label{thm2-dim}
%For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}. Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j,-\alpha_j}^{\theta_j}$ for some direction $\theta_j$.
For every $j=1,...,d$, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$. Then $\series{\Psi}_j(z)$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
\end{theorem}
\begin{proof}
We divide the proof into the following steps:
\begin{itemize}
\item[$(a)$] prove that $\hat{\psi}_j(\zeta_j)$ admits Laplace transform (see Lemma \ref{step a}) 
\item[$(b)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$
\item[$(c)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta_j}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
\end{itemize}

Step $(c)$ clearly follows from steps $(a)$ and $(b)$. In fact, from step $(b)$ and Theorem 3.1 $\Tilde{\psi}_j$ and $\hat{\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$. Then, by step $(a)$ we can Laplace transform both $\hat{\psi}_j$ and $\tilde{\psi}_j$.

We now prove step $(b)$: we want to show that $\series{\psi}_j=\borel_{\zeta}\series{\Psi}_j$ is a solution of $\hat{\mathcal{P}}_j\series{\psi}_j=0$. Recall that $\tilde{\Psi}_j$ is a trans-series, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_j$ is written in terms of the convolution product $\ast_{\alpha_j}$.

@@

\color{Turquoise}
\begin{lemma}\label{step a}
    Let $\hat{\psi}_j$ be the unique solution of $\hat{P}_j\hat{\psi}_j=0$, then it admits a Laplace transform. 
\end{lemma}

\begin{proof}
    We will prove the following: 
    \begin{itemize}
        \item there are only a finite number of singularities in the Borel plane, hence there is a direction which avoids all the singularities;
        \item the analytic continuation of $\hat{\psi}_j$ along that direction grows sub-exponentially. 
    \end{itemize}
    The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$. In fact, we can prove this statement using a perturbative method that goes back to Ecalle (see \cite{EcalleIII}, \cite[Section 2.5]{loday-Remy2011}). Let $\epsilon$ be a parameter and let $f_j(\zeta,\epsilon):=\sum_{k\geq 0}f_{j,k}(\zeta)\epsilon^k$ be a solution of  
    \[\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)+\epsilon\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r\right]f_j=0\]
    \textcolor{red}{such that $f_j(\zeta,1)=\hat{\psi}_j(\zeta)$}. We solve order by order in $\epsilon$: at order zero

>>>>

%\subsubsection{Regularity}

%We generalize the result of Delabere (Lemma~3.5 \cite{diverg-resurg-iii}) to deal with fractional power singularities:

%\begin{lemma}\label{lemma-3.5}
 %   Let $R_0>0$. Assume $f\in\mathcal{O}(\bar{D}(\infty,R_0))$ with $f(z)=O(z^{-\tau})$ at infinity for a certain $\tau\in\Q_{> 0}$, and let $M=\sup_{z\in D(\infty,R_0)} |f(z)|$. Then $\borel{f}$ is analytic on the Riemann surface of $\zeta^\tau$ and for every $\zeta$
  %  \begin{equation}
   %     |\borel{f}(\zeta)|\leq \frac{M}{\Gamma(\tau)}|\zeta|^\tau e^{\frac{|\zeta|}{R_0}}.
   % \end{equation}
%\end{lemma}

%\begin{proof}
 %   The Taylor series expansion of $f$, $\sum_{k\geq 0}f_k z^{-k-\tau}$ converges in $D(\infty,R_0)$. By Cauchy inequalities, $|f_k|\leq M R_0^{-k}$ for any $k\in\Z_{\geq 0}$. The formal Borel transform of $f$ reads
  %  \begin{align*}
   %     \borel{f}(\zeta)=\frac{\zeta^{\tau-2}}{\Gamma(\tau-1)}\ast\sum_{k\geq 0} f_k \frac{\zeta^k}{k!}
    %\end{align*}
   %and for every $\zeta\in\C$, $\sum_{k\geq 0}|f_k|\frac{|\zeta|^k}{k!}\leq M e^{\frac{|\zeta|}{R_0}}$. Therefore
   %\begin{align*}
    %   |\borel{f}(\zeta)|&=\Big|\frac{1}{\Gamma(\tau-1)} \int_0^\zeta (\zeta-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{t^k}{k!} dt\Big|\\
    %   &=\Big|\frac{\zeta^\tau}{\Gamma(\tau-1)} \int_0^1 (1-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{(\zeta t)^k}{k!} dt\Big|\\
   %    &\leq \frac{|\zeta|^\tau}{|\Gamma(\tau-1)|} \int_0^1 (1-t)^{\tau-1} M e^{\frac{|\zeta| t}{R_0}} dt\\
    %   &=M\frac{|\zeta|^\tau}{|\Gamma(\tau)|} e^{\frac{|\zeta|}{R_0}} 
   %\end{align*}

  % This ensures uniform convergence on any compact set of $\C$, thus $\borel{f}$ is analytic.
   %\color{Turquoise}
%In the last step of the bound, we argue as follows: if $\tau>1$ then $\sup_{t\in [0,1]]}(1-t)^{\tau-1}= 1$. If $\tau\in (0,1)$ we integrate by part 
%\begin{align*}
 %   \int_0^1 (1-t)^{\tau-1}  e^{\frac{|\zeta| t}{R_0}} dt&=-\frac{1}{\tau}(1-t)^{\tau}e^{\frac{|\zeta| t}{R_0}} \Big\vert_{t=0}^{t=1}+\frac{1}{\tau}\int_0^1(1-t)^\tau \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
  %  &\leq \frac{1}{\tau}+\frac{1}{\tau}\int_0^1 \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
   % &=\frac{1}{\tau}+\frac{1}{\tau} e^{\frac{|\zeta| t}{R_0}}\Big\vert_{t=0}^{t=1}\\
   % &=\frac{1}{\tau} e^{\frac{|\zeta| }{R_0}}
%\end{align*}
%   \color{black}
%\end{proof}

%\begin{lemma}\label{lemma-3.8}
 %   Let $a,b,c,m\geq 0$ and for $r=0,...,N$ let $R_r$ be a sequence of holomorphic functions in a neighborhood of infinity, real and positive on $\R^+$. Then, the convolution equation 
  %  \begin{equation}\label{eqn:convolution}
   %     \hat{W}=m+[a+b\xi]\ast\hat{W}+c \sum_{r=0}^N \borel(z^{-2}R_r(z^{-1}))\ast\hat{W}
   % \end{equation}
   % has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$. In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
%\end{lemma}

%We recall the following result which is a generalization of Lemma~3.8 in \cite{diverg-resurg-iii}:

%\begin{proof}
 %   If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution. If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization. Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
  %  \begin{equation}
        %\tilde{W}(z)=\frac{m}{z}+\left[\frac{a}{z}+\frac{b}{z^2}\right]\tilde{W}(z)+c\sum_{r=0}^{N}\frac{R_r(z^{-1})}{z^2}\tilde{W}(z)
   % \end{equation}
   % This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$). Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$. By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$. 
%\end{proof}

%\begin{lemma}\label{lemma-3.8bis}
 %Let $a_1,a_2,...,a_d,c,m\geq 0$ and $(\hat{R}_n)_{0\leq n\leq N}$ be a sequence of entire functions, real and positive on $\R^+$ with at most exponential growth of order $1$ at infinity. Then, the convolution equation 
 %   \begin{equation}\label{eqn:convolution-bis}
  %      \hat{W}=m+[a_1+a_2\xi+...+\frac{a_d}{(d-1)!}\xi^{d-1}]\ast\hat{W}+c\left(\hat{R}_0\ast\hat{W} +\sum_{n=1}^N\hat{R}_n\ast\hat{W}^n\right)
   %\end{equation}
    %has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$. In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
%\end{lemma}

%\begin{proof}
 %   If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution. If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization. Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
  %  \begin{equation}
   %     \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
    %\end{equation}
    %where $R_n(z)$ \textcolor{orange}{[maybe write these as $R_n(z^{-1})$ to match statement of ODE result]} are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$. This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$). Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$. By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$. 
%\end{proof}

%\begin{remark}
 %   Lemma \ref{lemma-3.8} and \ref{lemma-3.8bis} holds also when the convolution product $\ast$ is replaced by $\ast_p$ for every $p\in\C$. 
%\end{remark}

@@

\begin{theorem}\label{thm1-dim}
\textcolor{orange}{[Revise to match \texttt{reg-sing-volterra}]} In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
\begin{equation}\label{P-hat_j}
\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
\end{equation}
such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$ an open sectorial domain which closure contains $\alpha_j$.
\end{theorem}
\begin{proof}
It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of \textcolor{orange}{\texttt{reg-sing-volterra}}. Without loss of generality, we will consider $\hat{P}_1$.

\begin{align*}
    \lim_{\substack{\zeta_1\to 0\\ \zeta'\to 0}}\Big\vert \zeta_1\frac{Q(\alpha_1-\zeta')}{P(-\alpha_1-\zeta_1)}\Big\vert &=\lim_{\substack{\zeta_1\to 0\\ \zeta'\to 0}}\Big\vert \zeta_1\frac{Q(-\alpha_1-\zeta')}{\zeta_1(\zeta_1+\alpha_2)...(\zeta_1+\alpha_d)}\Big\vert\\
    &=\Big\vert \frac{Q(-\alpha_1)}{(\alpha_2-\alpha_1)...(\alpha_d-\alpha_1)}\Big\vert\\
    &=\Big\vert\frac{Q(-\alpha_1)}{P'(-\alpha_1)}\Big\vert
\end{align*}
in particular notice that $\tau_1:=\Big\vert\frac{Q(-\alpha_1)}{P'(-\alpha_1)}\Big\vert>0$ (since $Q(-\alpha_j)\neq 0$).

Since $P$ and $Q$ are polynomials, we get the following estimates:

\begin{align*}
    \sup_{|\zeta_1|\geq\delta}\Big\vert\frac{1}{P(-\alpha_1-\zeta_1)}\Big\vert=|P(-\alpha_1-\delta)|^{-1}
\end{align*}

\begin{align*}
    \sup_{|\zeta_1|\geq\delta}\Big\vert\frac{Q(-\alpha_1-\zeta_1)}{P(-\alpha_1-\zeta_1)}\Big\vert=\Big\vert\frac{Q(-\alpha_1-\delta)}{P(-\alpha_1-\delta)}\Big\vert
\end{align*}

We are left with the bounds on the kernel: following the notation of \textcolor{orange}{\texttt{reg-sing-volterra}}, we set

\begin{equation}
    K_{\text{soft}}(\zeta_1,s)=\sum_{r=0}^{d-1}\sum_{j=0}^{\infty}R_{r,j}\frac{(\zeta_1-s)^{j+1}}{j!}(-s-\alpha_1)^r
\end{equation}
where, since $R_r$ are holomorphic functions in some disk of radius $A$ centered at $\infty$, we define $R_r(z)=\sum_{j=0}^\infty R_{r,j}z^{-j}$ and $|R_{r,j}|\leq A^{-j}$. In particular,

\begin{align*}
    \Big\vert \sum_{j=0}^\infty \frac{R_{r,j}}{j!}(\zeta_1-s)^{j+1}\Big\vert \leq |\zeta_1-s| e^{\frac{|\zeta_1-s|}{A}}
\end{align*}

If $|\zeta_1|\geq\delta$ and $s\in\Omega_1$

\begin{align*}
    \Big\vert-\frac{Q(-s-\alpha_1)}{P(-\zeta_1-\alpha_1)}-\frac{K_{\text{soft}}(\zeta_1,s)}{P(-\alpha_1-\zeta_1)}\Big\vert&\leq  \Big\vert\frac{Q(-s-\alpha_1)}{P(-\zeta_1-\alpha_1)}\Big\vert+\Big\vert\frac{K_{\text{soft}}(\zeta_1,s)}{P(-\alpha_1-\zeta_1)}\Big\vert\\
    &\leq C+ |P(-\alpha_1-\delta)|^{-1} \sum_{r=0}^{d-1}\sum_{j=0}^{\infty} \Big\vert R_{r,j}\frac{(\zeta_1-s)^{j+1}}{j!}(-s-\alpha_1)^r\Big\vert\\
    &\leq C + |P(-\alpha_1-\delta)|^{-1} \sum_{r=0}^{d-1}|\zeta_1-s|e^{|\zeta_1-s|/A} |s-\alpha_1|^r
\end{align*}

In particular, for every $\zeta_1,s\in\Omega_1$

\begin{align*}
    \Big\vert \zeta_1 \frac{K_{\text{soft}}(\zeta_1,s)}{P(-\alpha_1-\zeta_1)}\Big\vert&\leq |\zeta_1-s| e^{|\zeta_1-s|/A} \sum_{r=0}^{d-1}\frac{|s-\alpha_1|^r}{|(\zeta_1+\alpha_2)...(\zeta_1+\alpha_d)|}\\
\end{align*}

\textcolor{magenta}{[to conclude, we need assumption on how $s$ and $\zeta_1$ respectively move in $\Omega_1$. ]}

@@

Therefore, there exists a unique solution

\begin{equation}\label{eqn:slight_solution}
    \psi_1(\zeta_1)=\zeta_1^{\tau_1-1}+f_1(\zeta_1)
\end{equation}
 and $f_1\in\mathcal{HL}^{\infty}_{\tau_1,1/A}(\Omega_1)$.

@@

\begin{corollary}\label{cor:existence_Laplace}
    Under the assumption of Theorem \ref{thm1-dim}, the function $\hat{\psi}_j$ defined in Equation \eqref{eqn:slight_solution} admits a Laplace transform. 
\end{corollary}

\begin{lemma}
 Let $\hat{\psi}_j$ be a solution of $\hat{P}_j\hat{\psi}_j=0$ for every $j=1,...,d$ and $\hat{P}_j$ defined in \eqref{P-hat_j}. Let $\Psi_j=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j$ be the Laplace transform of $\hat{\psi}_j$, for $j=1,...,d$ and for a suitable direction $\theta_j$, then $\mathcal{P}\Psi_j=0$.   
\end{lemma}

@@

\begin{theorem}\label{thm2-dim}
%For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}. Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j,-\alpha_j}^{\theta_j}$ for some direction $\theta_j$.
For every $j=1,...,d$, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$. Then $\series{\Psi}_j(z)$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
\end{theorem}
\begin{proof}
We divide the proof into the following steps:
\begin{itemize}
\item[$(a)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$
\item[$(b)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta_j}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
\end{itemize}

Step $(b)$ clearly follows from Corollary \ref{cor:existence_Laplace} and step $(a)$. In fact, from step $(a)$ and Theorem \ref{thm1-dim}, $\Tilde{\psi}_j$ and $\hat{\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$. Then, by Corollary \ref{cor:existence_Laplace} we can Laplace transform both $\hat{\psi}_j$ and $\tilde{\psi}_j$.

We now prove step $(a)$: we want to show that $\series{\psi}_j=\borel_{\zeta}\series{\Psi}_j$ is a solution of $\hat{\mathcal{P}}_j\series{\psi}_j=0$. Recall that $\tilde{\Psi}_j$ is a trans-series, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_j$ is written in terms of the convolution product $\ast_{\alpha_j}$.

@@

%\color{Turquoise}
%\begin{lemma}\label{step a}
%    Let $\hat{\psi}_j$ be the unique solution of $\hat{P}_j\hat{\psi}_j=0$, then it admits a Laplace transform. 
%\end{lemma}

%\begin{proof}
 %   We will prove the following: 
  %  \begin{itemize}
   %     \item there are only a finite number of singularities in the Borel plane, hence there is a direction which avoids all the singularities;
    %    \item the analytic continuation of $\hat{\psi}_j$ along that direction grows sub-exponentially. 
    %\end{itemize}
    %The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$. In fact, we can prove this statement using a perturbative method that goes back to Ecalle (see \cite{EcalleIII}, \cite[Section 2.5]{loday-Remy2011}). Let $\epsilon$ be a parameter and let $f_j(\zeta,\epsilon):=\sum_{k\geq 0}f_{j,k}(\zeta)\epsilon^k$ be a solution of  
   % \[\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)+\epsilon\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r\right]f_j=0\]
   % \textcolor{red}{such that $f_j(\zeta,1)=\hat{\psi}_j(\zeta)$}. We solve order by order in $\epsilon$: at order zero

    %\begin{align*}
     %   &P(-\zeta)f_{j,0}+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)f_{j,0}=0\\
      %  &-P'(-\zeta)f_{j,0}+P(-\zeta)\partial_\zeta f_{j,0}+Q(-\zeta)f_{j,0}=0\\
       % &P(-\zeta)\partial_\zeta f_{j,0}=P'(-\zeta)f_{j,0}-Q(-\zeta)f_{j,0}
    %\end{align*}
    %If $\zeta\neq\alpha_k$ for $k=1,...,d$ we can solve the first order equation and for $a\neq\alpha_k$
    %\begin{align*}
     %   f_{j,0}&=f_{j,0}(a)\cdot \exp\left(\int_a^{\zeta}\frac{P'(-t)-Q(-t)}{P(-t)}dt\right)\\
      %  &=f_{j,0}(a)\cdot \frac{P(-a)}{P(-\zeta)}\exp\left(-\int_a^{\zeta}\frac{Q(-t)}{P(-t)}dt\right)
    %\end{align*}
    %Therefore, $f_{j,0}$ is singular at $\zeta=\alpha_k$ for every $k=1,...,d$ (or equivalently, at $\zeta_j=\alpha_k-\alpha_j$). Then, for $n\geq 1$
